---
title: qmd-pptx-template
subtitle: Here is the subtitle
author: Author 1, Author 2
date: last-modified
date-format: long
footer: this is the global footer
format: 
  pptx:
    incremental: true
    reference-doc: pptx-template/epicentre-pptx-template.pptx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)

library(fs)         # work with path
library(here)       # create relative paths
library(rio)        # import files
library(janitor)    # data cleaning
library(lubridate)  # date handling
library(tidyverse)  # data science 

```

# Section 1 

## Title and Content slide

This list of item is incremental - change to `incremental: false` in the `YAML` to turn it off

- list 1 
- list 2
- list 3

## Speakers notes 

You can add speaker notes with

```{r, eval = FALSE, echo = TRUE}

::: {.notes}
Speaker notes go here.
:::
  
```

::: {.notes}
Speaker notes go here.
:::


## Two Content slide

:::: {.columns}

::: {.column width="40%"}
There can be content ... 
:::

::: {.column width="60%"}
... split in different columns 
:::

::::


# Section 2 

## Comparison slide 

:::: {.columns}

::: {.column width="40%"}
Text here with image/table next to it 
:::

::: {.column width="60%"}
```{r, eval = TRUE, echo = FALSE, width = 50}
head(iris) %>% knitr::kable()
```
:::

::::

## Content with Caption slide 

There is text above a graph or a table 

```{r, eval = TRUE, echo = FALSE}
ggplot(data = iris, 
       aes(x = Sepal.Length, y = Sepal.Width)) + 
  geom_point()

```


--- 

::: {.notes}
Blank slide to get the final slide
:::


