---
title: qmd-pptx-template
subtitle: Here is the subtitle
author: Author 1 Author 2
institute: EpiDS - Epicentre, Paris
date: last-modified
date-format: long
footer: this is the global footer
format: 
  revealjs:
    theme: css/epicentre_revealjs_style.scss
    logo: img/epicentre_logo.png
    incremental: false
    slide-number: c/t
    overview: true
    progress: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)

library(fs)         # work with path
library(here)       # create relative paths
library(rio)        # import files
library(janitor)    # data cleaning
library(lubridate)  # date handling
library(tidyverse)  # data science 

```

# Revealjs basics

## Incremental list

This list of item is not incremental 

- list 1 
- list 2
- list 3

change to `incremental: true` in the `YAML` to turn it off or use 

```{r, eval = FALSE} 

::: {.incremental}
- item 1
- item 2
- item 3
:::
  
```

## Slides with pause 

You can add pauses 

. . .

using `. . .` surrounded with empty lines


## Multiple columns

:::: {.columns}

::: {.column width="40%"}
There can be content ... 
:::

::: {.column width="60%"}
... split in different columns 
:::

::::

## Slide Title {.scrollable}

`{.scrollable}` will make the slide scrollable if it has a lot of content 

- 1
- 2
- 3
- 4
- 5
- 6
- 7
- 8
- 9
- 10

## Slide Title {.smaller}

`{.smaller}` will make the slide content smaller 


## Speakers notes 

You can add speaker notes with

```{r, eval = FALSE, echo = TRUE}

::: {.notes}
Speaker notes go here.
:::
  
```

and press `S` to go in speaker view 

::: {.notes}
Speaker notes go here.
:::

## Asides & Footnotes 

- item 1
- item 2
- item 3 ^[A footnote]

You sill notice the EPICENTRE logo shared across the slides. this is set in the `YAML`

::: aside
And there is also asides notes like this one 
:::

## Footer and logo 

There is a global footer assigned in the `YAML` that is shared across slides. You can also include a custom one 

::: footer
Like this one 
:::

# Code blocks

## Code chunks
By default are chunks are `echo` but not executed. Use the chunks option to modify this. 

- They are written as `#|` above source code.
- You can also change the location of the source code output

```{r}
#| echo: fenced
#| fig-cap: "This is the caption of this figure"
#| eval: true
#| output-location: column

ggplot(data = iris, aes(y = Petal.Length, 
                        x = Petal.Width, 
                        col = Species)) +
  
  geom_point()

```

## Figure size {.smaller}

It will have to be manually set using `width` and `height` chunks options for `R` (`knitr`) output

```{r}
#| eval: true
head(iris) %>% knitr::kable()
```


## Tabsets 

:::{.important}
You can create different tabs in a slide and highligth stuff with a call out `{.important}`
:::

::: {.panel-tabset}

### Tab A

Content for `Tab A`

### Tab B

Content for `Tab B`

:::
