---
title: "qmd-template"
subtitle: 'EpiDS team - Epicentre, Paris'
author: 
  - name: Author 1
    email: email.author.1@epicentre.msf.org
  - name: Author 2
    email: email.author.2@epicentre.msf.org
date: last-modified
date-format: long

format:
  html:
    title-block-banner: true
    embed-resources: true
    theme: 
      - cosmo
      - css/epicentre_qmd_style.scss
    smooth-scroll: true
    code-fold: show
    code-tools: true
    toc: true
    toc-location: left
    toc-float: true
    toc-collapsed: true
    callout-appearance: minimal
comments:
  hypothesis: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)

library(fs)         # work with path
library(here)       # create relative paths
library(rio)        # import files
library(janitor)    # data cleaning
library(lubridate)  # date handling
library(tidyverse)  # data science 

```

# Primary title

1. *Italic* and **Bold** will turn out like this

2. Tooltip are trickier to use than in a normal `.Rmd` not set-up here yet

3. Inline coding will turn out `like this`

4. You can also annotate and comment the text. This requires an account on [Hypothes.is](https://web.hypothes.is/)

## Secondary title

::: {.callout-note}
**This is a Note** using `{.callout-note}`
:::

::: {.callout-caution}
**This is a caution** using `{.callout-caution}`. They can be collapsed using `collapse="true"` 
:::

::: {.callout-important}
**This is an important note** using `{.callout-important}`
:::

> This is a `blockquote` made using `>` 

### Tertiary title

```{r, eval = FALSE}
# Use this global options in YAML to hide all code chunks

---
execute: 
  echo: false 
---
  
```
